---
title: "Open Source Projects & Libraries"
pagetitle: "Projects | Anthony Faustine"
description-meta: "Open-source ML libraries and toolkits for forecasting, load monitoring, and production machine learning systems."

format:
  html:
    body-class: "projects"
    page-layout: full
    include-in-header:
      - text: |
          <link rel="stylesheet" href="projects.css">

toc: false
---

```{r setup, include=FALSE}
library(yaml)
projects_data <- yaml::read_yaml("data.yml")
```

::: {.hero-section .mb-5}
# Open Source Projects & Libraries

I build production-grade ML libraries that solve real problems. These projects span my evolution: from foundational research through enterprise production systems, with a commitment to community maintenance and long-term stewardship.

:::

```{=html}
<div class="projects-timeline">
```

```{r, include=FALSE}
# Group projects by status
status_order <- c("Active", "Maintained", "Community")
projects_by_status <- list()

for (status in status_order) {
  projects_by_status[[status]] <- list()
  for (proj in projects_data$projects) {
    if (proj$status == status) {
      projects_by_status[[status]][[length(projects_by_status[[status]]) + 1]] <- proj
    }
  }
}
```

```{r, results='asis', echo=FALSE}
for (status in status_order) {
  projects <- projects_by_status[[status]]
  if (length(projects) == 0) next

  color <- projects_data$status_colors[[status]]

  cat(sprintf('<div class="timeline-section">\n'))
  cat(sprintf('<div class="status-header" style="border-color: %s;">\n', color))
  cat(sprintf('<span class="status-badge" style="background-color: %s;">%s</span>\n', color, status))
  cat(sprintf('<span class="project-count">%d</span>\n', length(projects)))
  cat('</div>\n')

  for (proj in projects) {
    cat(sprintf('<div class="timeline-entry" style="border-left-color: %s;">\n', color))
    cat(sprintf('<div class="timeline-dot" style="background-color: %s;"></div>\n', color))

    cat('<div class="project-content">\n')
    cat(sprintf('<div class="project-year">%s</div>\n', proj$year))
    cat(sprintf('<h3 class="project-name">%s</h3>\n', proj$name))
    cat(sprintf('<p class="project-description">%s</p>\n', proj$description))
    cat(sprintf('<div class="project-highlight">💡 %s</div>\n', proj$highlight))

    # Links
    cat('<div class="project-links">\n')
    for (link in proj$links) {
      cat(sprintf('<a href="%s" class="project-link" title="%s">\n', link$url, link$label))
      cat(sprintf('<i class="bi bi-%s"></i> %s</a>\n', link$icon, link$label))
    }
    cat('</div>\n')

    cat('</div>\n')
    cat('</div>\n')
  }

  cat('</div>\n')
}
```

```{=html}
</div>
```

---

## Get Involved

These projects welcome contributions, feedback, and collaborations. Whether you're:
- Using these tools in your own work
- Reporting bugs or suggesting features
- Contributing code or documentation
- Citing in research

Please reach out via [GitHub](https://github.com/sambaiga) or [email](mailto:sambaiga@gmail.com).

## Status Legend

- **Active**: Actively developed, regular updates, production-ready
- **Maintained**: Stable, occasional updates, community contributions welcome
- **Community**: Community-driven, foundational research, open to contributions
